\begin{thebibliography}{1}

\bibitem {bib_constraint} Simonis, H., 2005, October. Sudoku as a constraint problem. In CP Workshop on modeling and reformulating Constraint Satisfaction Problems (Vol. 12, pp. 13-27). Citeseer.
\linebreak

\bibitem {bib_search}	Gayatri, P., Performance Analysis of Various Uninformed and Informed Search Strategies on 8 Puzzle Problems-A Case Study.
\linebreak



\bibitem {bib_madnumbers}	D. NAKAMURA, "The man behind those maddening numbers," 24 May 2009. [Online]. Available: \url{https://www.latimes.com/archives/la-xpm-2009-may-24-adna-sudoku24-story.html} (Accessed: 10 April 2022).
\linebreak

\bibitem {bib_euler} D. Garisto, "Euler’s 243-Year-Old ‘Impossible’ Puzzle Gets a Quantum Solution," 10 January 2022. [Online]. Available: \url{https://www.quantamagazine.org/eulers-243-year-old-impossible-puzzle-gets-a-quantum-solution-20220110/} (Accessed: 10 April 2022).

\bibitem {bib_rateddataset} D. Radcliffe, "3 million Sudoku puzzles with ratings," 2020. [Online]. Available: \url{https://www.kaggle.com/datasets/radcliffe/3-million-sudoku-puzzles-with-ratings} (Accessed: 10 April 2022).

\bibitem {bib_cnndataset} K. Park, "1 million Sudoku games," 2017. [Online]. Available: \url{https://www.kaggle.com/datasets/bryanpark/sudoku} (Accessed: 10 April 2022).

\bibitem {bib_memoryeval} robguinness, "How do I profile memory usage in Python?," 14 November 2018. [Online]. Available: \url{https://stackoverflow.com/questions/552744/how-do-i-profile-memory-usage-in-python/53301648#53301648} (Accessed: 10 April 2022).

\bibitem {bib_memoryeval}A comparison of a genetic algorithm and a depth first
search algorithm applied to Japanese, Wouter Wiggers
Faculty of EECMS, University of Twente.

\end{thebibliography}